**Urinary Vitamin D Binding Protein as a Potential Biomarker for Nephropathy in Patients at risk for Type 2 Diabetes**: The Prospective Metabolism and Islet Cell Evaluation (PROMISE) cohort study.

### 2017-02-17 doc/adaAbstract.Rmd
ACR boxplots

ACR
---
```{r acr boxplot}

# Box plot of uVDBP in different albuminuria categories

ds %>% 
  filter(fVN == "Baseline") %>% 
  select(acr_status, udbpCrRatio) %>%
  na.omit() %>%
  box_plot("acr_status", "log(udbpCrRatio)", 
            "Albuminuria",
            "log uVDBP:Creatinine")

# Boxplot of ACR in uVDBP categories
ds1 %>% 
  select(UDBP_status, ACR) %>% 
  na.omit() %>% 
  box_plot("UDBP_status", "log(ACR)",
           "Urinary VDBP status",
           "log urine albumin-to-creatinine ratio (mg/mmol)")

# Values
table_value(ds1, by = "acr_status")

anova <- aov(formula = log(udbpCrRatio)~acr_status, data = ds1)
summary(anova)
TukeyHSD(anova)
rm(anova)
```

@@

ds %>% 
  filter(fVN == "Baseline") %>% 
  select(ACR, udbpCrRatio) %>% 
  na.omit() %>% 
  scatter_plot("log(ACR)", "log(udbpCrRatio)",
               "log Albumin:Creatinine Ratio",
               "log UDBP:Creatinine") +
  geom_smooth(method = lm, colour = "grey50")

@@

eGFR
----
```{r eGFR boxplot}

@@

# Values
table_value(ds1, by = "eGFR_status")

>>>>

## ACR

```{r acr}

# Box plot of uVDBP in different albuminuria categories
ds %>% 
  filter(fVN == "Baseline") %>% 
  select(acrStatus, udbpCrRatio) %>%
  na.omit() %>%
  box_plot("acrStatus", "log(udbpCrRatio)", 
            "Albuminuria",
            "log uVDBP:Creatinine")

# Boxplot of ACR in uVDBP categories
dsBase %>% 
  select(UDBPStatus, ACR) %>% 
  na.omit() %>% 
  box_plot("UDBPStatus", "log(ACR)",
           "Urinary VDBP status",
           "log Urine ACR (mg/mmol)")

# ANOVA
anova <- aov(formula = log(udbpCrRatio)~acr_status, data = ds1)
summary(anova)
TukeyHSD(anova)
rm(anova)
```

@@

ds %>% 
  filter(fVN == "Baseline") %>% 
  select(ACR, udbpCrRatio) %>% 
  na.omit() %>% 
  scatter_plot("log(ACR)", "log(udbpCrRatio)",
               "log Albumin:Creatinine Ratio",
               "log UDBP:Creatinine",
               line = TRUE)

@@

## eGFR

```{r eGFR boxplot}

@@
